---
title: "old_code"
author: "Jen Richmond"
date: "28/06/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# DEALING WITH ATTENTION SCORES

Select just variables related to attention checks/scores. Make score data long. 
```{r}
attention_scores <- analysable_data %>%
  select(end_date, progress, response_id, gender, age_in_years, faculty_of_study, research_experience, group, starts_with("attention_attempt"), starts_with("score")) 


attention_scores_long <- attention_scores %>%
  pivot_longer(names_to = "test_attempt", values_to = "score", score_attempt_1:score_attempt_3) 

```

Trying to summarise how many times each participant attempted test. 

Add a new column testTF that add TRUE/FALSE according to whether the score > 0 or is.na. Turn that variable into a logical. Because logical (TRUEFALSE) are coded as 1, 0, you can sum them. Group by response id, and sum how many TRUES (ie how many tests each participant did)


```{r}

attention_attempts <- attention_scores_long %>%
  mutate(testTF = case_when(score >= 0 ~ "TRUE",
                            is.na(score) ~ "FALSE"))

glimpse(attention_attempts)

attention_attempts$testTF <- as.logical(attention_attempts$testTF)

attention_attempts %>%
  group_by(response_id) %>%
 summarise(number_of_tests = sum(testTF))
  

```



NEXT STEPS

- For participants who are taking 3 attempts, are they scoring 5+ in the last attempt? (i.e. should they be included or excluded) (tip use **filter** to get rid of those who don't pass attention check)


```{r}

attention_attempts %>% filter(test_attempt == "score_attempt_3") %>%
  filter(testTF == "TRUE") %>%
  filter(score <= 4)

```

```{r}

analysable_data %>% filter(score_attempt_3 > 5)

```

```{r}

included_data <- analysable_data %>% filter(response_id != "R_WimZTSSd9X5s26B", response_id != "R_xrRKzEUE3P5jUD7", response_id != "R_2CeygpVUy7RSuOp")

```

Once we have determined how many of these N= 20 should be included, then need to
- make new variables (tip use **mutate**) for averaged scores for 
  + attitudes (across 5 items)
  + intentions (across 4 items)
  
```{r}

averaged_data <-
included_data %>% 
  rowwise() %>%
  mutate(mean_attitude=mean(c(attitude_overall_1, attitude_design_1, attitude_data_1, attitude_analyses_1, attitude_access_1, na.rm = TRUE))) %>%
  mutate(mean_intention=mean(c(intention_design_1, intention_data_1, intention_analyses_1, intention_access_1, na.rm = TRUE)))

```
 
 Get summary stats
 - does there look like there are group differences in M perception, attitude and intention scores (tip = use **group_by** + **summarise**)

```{r}

data_summary <-
averaged_data %>%
  group_by(group) %>%
    summarise(perception_by_group_mean = mean(perception_1, na.rm = TRUE),
              attitude_by_group = mean(mean_attitude, na.rm = TRUE),
              intention_by_group = mean(mean_intention, na.rm = TRUE),
              manipulation_gf_by_group = mean(manipulation_check_gf_1, na.rm = TRUE),
              manipulation_lf_by_group = mean(manipulation_check_lf_1, na.rm = TRUE))

```

**ggplot** group differences in... x = group y = perception/attitude/intention

- perception
- average attitude
- average intention
- manipulation check positive
- manipulation check negative

NOTE: make plots with both raw data and means


Test whether those group difference are significant

Perception

```{r}

perception_summary <- averaged_data %>%
  group_by(group) %>%
  summarise(mean = mean(perception_1), 
            sd = sd(perception_1), 
            n = n(), 
            stderr = sd / sqrt(n))
            
  print(perception_summary)
  
```

```{r}

averaged_data %>%
  ggplot(aes(x = group, y = perception_1, fill = group)) +
    geom_col() +
   geom_errorbar(aes(ymin = mean - stderr, ymax = mean + stderr), 
                size = .3, #thinner lines
                width = .2) #narrower error bar
    theme_classic()

```

Attitude

```{r}

attitude_summary <- averaged_data %>%
  group_by(group) %>%
  summarise(mean = mean(mean_attitude, na.rm = TRUE), 
            sd = sd(mean_attitude, na.rm = TRUE), 
            n = n(), 
            stderr = sd / sqrt(n))
            
  print(attitude_summary)
  
```





