---
title: "4_study1plots"
author: "Jen Richmond"
date: "13/07/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(here)
library(ggeasy)
```


```{r}
clean_data <- read_csv(here("data", "dateStudy1data_clean.csv"))
```

```{r}

summary_data <- read_csv(here("data", "summary_data.csv"))

```

Categorical variable: group
Continuous variable: perception_1, mean_att, mean_int

#Mean ratings for gain and loss manipulation check by group

Column graph:

```{r}

```

Geom jitter plot:

```{r}

```

#Mean ratings for perception by group

Column graph:

```{r}

summary_data <- summary_data %>%
  mutate(group = factor(group, 
                        levels = c(1, 2),
                        labels = c("gain", "loss")))

summary_data %>%
  ggplot(aes(x = group, y = per_M,)) +
  geom_col() +
  scale_y_continuous(limits = c(0,5)) +
  geom_errorbar(aes(ymin=per_M-perStdErr, ymax=per_M+perStdErr),
                size=.3, 
                width=.2) +
  theme_classic() +
  labs(title = "Mean perception ratings by group")

```

Geom jitter plot:

```{r}

clean_data <- clean_data %>%
  mutate(group = factor(group, 
                        levels = c(1, 2),
                        labels = c("gain", "loss")))

clean_data %>%
  group_by(group) %>%
  ggplot(aes(x = group, y = perception_1)) +
  geom_jitter() +
  scale_y_continuous(limits = c(0,5)) +
  theme_classic() +
  labs(title = "Mean perception ratings by group")

```

#Mean ratings for attitude by group

Column graph:

```{r}

summary_data <- summary_data %>%
  mutate(group = factor(group, 
                        levels = c(1, 2),
                        labels = c("gain", "loss")))

summary_data %>%
  ggplot(aes(x = group, y = att_M)) +
  geom_col() +
  scale_y_continuous(limits = c(0,5)) +
  geom_errorbar(aes(ymin=att_M-attStdErr, ymax=att_M+attStdErr),
                size=.3, 
                width=.2) +
  theme_classic() +
  labs(title = "Mean attitude ratings by group")

```

Geom jitter plot:

```{r}

clean_data <- clean_data %>%
  mutate(group = factor(group, 
                        levels = c(1, 2),
                        labels = c("gain", "loss")))

clean_data %>%
  group_by(group) %>%
  ggplot(aes(x = group, y = mean_att)) +
  geom_jitter() +
  scale_y_continuous(limits = c(0,5)) +
  theme_classic() +
  labs(title = "Mean attitude ratings by group")

```

#Mean ratings for intention by group

Column graph:

```{r}

summary_data <- summary_data %>%
  mutate(group = factor(group, 
                        levels = c(1, 2),
                        labels = c("gain", "loss")))

summary_data %>%
  ggplot(aes(x = group, y = int_M)) +
  geom_col() +
  scale_y_continuous(limits = c(0,5)) +
  geom_errorbar(aes(ymin=int_M-intStdErr, ymax=int_M+intStdErr),
                size=.3, 
                width=.2) +
  theme_classic() +
  labs(title = "Mean intention ratings by group")

```

Geom jitter plot:

```{r}

clean_data <- clean_data %>%
  mutate(group = factor(group, 
                        levels = c(1, 2),
                        labels = c("gain", "loss")))

clean_data %>%
  group_by(group) %>%
  ggplot(aes(x = group, y = mean_int)) +
  geom_jitter() +
  scale_y_continuous(limits = c(0,5)) +
  theme_classic() +
  labs(title = "Mean attitude ratings by group")

```
