---
title: "4_study1plots"
author: "Jen Richmond"
date: "13/07/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(here)
library(ggeasy)
```


```{r}
clean_data <- read_csv(here("data", "dateStudy1data_clean.csv"))
```

```{r}

summary_data <- read_csv(here("data", "summary_data.csv"))

```

Categorical variable: group
Continuous variable: perception_1, mean_att, mean_int

#Mean ratings for gain manipulation check by group

Column graph:

```{r}

manipcheck <- manipcheck %>%
  mutate(group = factor(group, 
                        levels = c(1, 2),
                        labels = c("gain", "loss")))

manipcheck %>%
    ggplot(aes(x = group, y = mean)) +
    geom_col() +
    scale_y_continuous(expand = c(0,0),
                       limits = c(0,5)) +
    geom_errorbar(aes(ymin=mean-StdErr, ymax=mean+StdErr),
                  size=.3, 
                  width=.2) +
  theme_classic() +
  labs(title = "To what extent did the information stress the positive benefits of \nadopting open science practices?")

```
> JR: things to work out how to fix in this plot...
1. how to make the bars sit on the x axis
2. how to make bars less wide
3. add more descriptive x and y axis labels
4. wrap title so it will fit


Geom jitter plot:

```{r}

clean_data <- clean_data %>%
  mutate(group = factor(group, 
                        levels = c(1, 2),
                        labels = c("gain", "loss")))

clean_data %>%
  group_by(group) %>%
  ggplot(aes(x = group, y = manipulation_check_gf_1)) +
  geom_jitter() +
  scale_y_continuous(limits = c(0,5)) +
  theme_classic() +
  labs(title = "To what extent did the information stress the positive benefits of adopting open science practices?")

```

> JR: things to work out how to fix in this plot...
1. how to make the group not be 1.0, 1.5, 2.0 (ideally you want this to say gain loss)
2. how to make jitter more constrained
3. add more descriptive x and y axis labels
4. wrap title so it will fit



#Mean ratings for loss manipulation check by group

Column graph:

```{r}

manipcheck <- manipcheck %>%
  mutate(group = factor(group, 
                        levels = c(1, 2),
                        labels = c("gain", "loss")))

manipcheck %>%
  ggplot(aes(x = group, y = mean)) +
  geom_col() +
  scale_y_continuous(limits = c(0,5)) +
  geom_errorbar(aes(ymin=mean - StdErr, ymax=mean + StdErr),
                size=.3, 
                width=.2) +
  theme_classic() +
  labs(title = "To what extent did the information stress the negative consequences of not adopting open science practices?")

```

> JR: things to work out how to fix in this plot...
1. this one doesn't work, only gives 1 bar?? shoudl look like gain bar plot above
2. maybe it makes sense to put both gain and loss manipulation check on a single plot, can yu do that with facet_wrap()?


Geom jitter plot:

```{r}

clean_data <- clean_data %>%
  mutate(group = factor(group, 
                        levels = c(1, 2),
                        labels = c("gain", "loss")))

clean_data %>%
  group_by(group) %>%
  ggplot(aes(x = group, y = manipulation_check_lf_1)) +
  geom_jitter() +
  scale_y_continuous(limits = c(0,5)) +
  theme_classic() +
  labs(title = "To what extent did the information stress the negative consequences of not adopting open science practices?")

```

> JR: things to work out how to fix in this plot...
1. how to make jitter more constrained
2. add more descriptive x and y axis labels
3. wrap title so it will fit

#Mean ratings for perception by group

Column graph:

```{r}
# note you shouldn't have to do this everytime, once you convert group to factor with labels in the summary dataframe, and use assignment <- to apply the change to the dataframe it will stick
summary_data <- summary_data %>%
  mutate(group = factor(group, 
                        levels = c(1, 2),
                        labels = c("gain", "loss")))

summary_data %>%
  ggplot(aes(x = group, y = per_M,)) +
  geom_col() +
  scale_y_continuous(limits = c(0,5)) +
  geom_errorbar(aes(ymin=per_M-perStdErr, ymax=per_M+perStdErr),
                size=.3, 
                width=.2) +
  theme_classic() +
  labs(title = "Mean perception ratings by group")

```

> JR: things to work out how to fix in this plot...
1. this one doesn't work, only gives 1 bar?? 
2. more descriptive x and y axis labels
3. bar sits on x axis


Geom jitter plot:

```{r}

clean_data <- clean_data %>%
  mutate(group = factor(group, 
                        levels = c(1, 2),
                        labels = c("gain", "loss")))

clean_data %>%
  group_by(group) %>%
  ggplot(aes(x = group, y = perception_1)) +
  geom_jitter() +
  scale_y_continuous(limits = c(0,5)) +
  theme_classic() +
  labs(title = "Mean perception ratings by group")

```

> JR: things to work out how to fix in this plot...
1. more constrained jitter
2. more descriptive x and y axis labels
3. more accurate title, this isn't means



#Mean ratings for attitude by group

Column graph:

```{r}

summary_data <- summary_data %>%
  mutate(group = factor(group, 
                        levels = c(1, 2),
                        labels = c("gain", "loss")))

summary_data %>%
  ggplot(aes(x = group, y = att_M)) +
  geom_col() +
  scale_y_continuous(limits = c(0,5)) +
  geom_errorbar(aes(ymin=att_M-attStdErr, ymax=att_M+attStdErr),
                size=.3, 
                width=.2) +
  theme_classic() +
  labs(title = "Mean attitude ratings by group")

```
> JR: things to work out how to fix in this plot...
1. this one doesn't work, only gives 1 bar?? 
2. more descriptive x and y axis labels
3. bars sits on x axis


Geom jitter plot:

```{r}

clean_data <- clean_data %>%
  mutate(group = factor(group, 
                        levels = c(1, 2),
                        labels = c("gain", "loss")))

clean_data %>%
  group_by(group) %>%
  ggplot(aes(x = group, y = mean_att)) +
  geom_jitter() +
  scale_y_continuous(limits = c(0,5)) +
  theme_classic() +
  labs(title = "Mean attitude ratings by group")

```

#Mean ratings for intention by group

Column graph:

```{r}

per_att_int <- per_att_int %>%
  mutate(group = factor(group, 
                        levels = c(1, 2),
                        labels = c("gain", "loss")))

per_att_int %>%
  ggplot(aes(x = group, y = int_M)) +
  geom_col() +
  scale_y_continuous(expand = c(0,0),
                     limits = c(0,5)) +
  geom_errorbar(aes(ymin=int_M-intStdErr, ymax=int_M+intStdErr),
                size=.3, 
                width=.2) +
  theme_classic() +
  labs(title = "Mean intention ratings by group")

```

Geom jitter plot:

```{r}

clean_data <- clean_data %>%
  mutate(group = factor(group, 
                        levels = c(1, 2),
                        labels = c("gain", "loss")))

clean_data %>%
  group_by(group) %>%
  ggplot(aes(x = group, y = mean_int)) +
  geom_jitter() +
  scale_y_continuous(limits = c(0,5)) +
  theme_classic() +
  labs(title = "Mean attitude ratings by group")

```
