---
title: "cleanQualtricsdata"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(here)
```


```{r}
datatest <-  read_csv(here("data", "jennytest.csv"))
```


# select just variables of interest

Make a dataframe with just useful variables


Selecting just participant details, ratings of perception, attitude, intention, manipulation checks and attention variables. Lets keep attention and other variables together for now. 
```{r}

data_select <- datatest %>%
  select(end_date, progress, response_id, group, gender, age_in_years, faculty_of_study, research_experience, perception_1, starts_with("attitude"), starts_with("intention"), manipulation_check_gf_1, manipulation_check_lf_1, starts_with("attention_attempt"),  starts_with("score"))

```


# filter out participants who didn't complete the whole survey

Looks like there are some value of < 100 in the progress column. Filter out those that didn't complete the survey. 

```{r}

progress_filtered <- data_select %>%
  filter(progress == "100")

```

# create new exclude column for attention scores 

I think it is easier to do this without making the data long...

use mutate and case_when to create a new column that puts "include" or "exclude" in the column, depending on performance on score_attempt 1, 2 and 3. If they get >-5 on 1, 2, or, 3 then 'include', if they get <=4 on attempt 3 then 'exclude'

http://jenrichmond.rbind.io/post/mutate-and-if-else-to-create-new-variables/ 

```{r}

exclude_column <- progress_filtered %>%
  mutate(exclusion = case_when(score_attempt_1 >= 5 ~ 'Include',
                               score_attempt_2 >= 5 ~ 'Include',
                               score_attempt_3 >= 5 ~ 'Include',
                               TRUE ~ 'Exclude'))

```

# filter out those that get exclude in above column 

Filter out those excluded for attention fail, then drop atten/score columns from the dataframe using select(). 

```{r}

attention_filtered <- exclude_column %>%
  filter(exclusion == "Include")

important_data <- attention_filtered %>%
  select(end_date, progress, response_id, group, gender, age_in_years, faculty_of_study, research_experience, perception_1, starts_with("attitude"), starts_with("intention"), manipulation_check_gf_1, manipulation_check_lf_1, exclusion)

```

#  exclude participants who didn't answer enough attitude/intention qs 

from prereg: If a participant does not complete the single perceived severity question, at least 3 of 5 attitude questions, or at least 2 of 4 implementation intenxstion questions, the participant’s response will be excluded from the analysis for that particular dependent variable. 

Need to count how many NAs each participant has across perception, attitude and intention qs and exclude if more than 0 (perception) or 2 (attitude and intention)

```{r}

na_count <- important_data %>%
  rowwise %>%
  summarise(NA_per_row = sum(is.na(important_data)))

  count(perception_1, wt = NULL, sort = FALSE, name = NULL)
  sum(is.na(perception_1))
  sum(complete.cases(important_data))
  sum(perception_1 == value, na.rm=FALSE)
  apply(perception_1, MARGIN = 1, function(x) sum(is.na(x)))

```





